Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-05-15 paper/ms.tex
Add ref to 2020 pattern speed paper

The expectation that a dark matter halo acts to slow down a bar is in
conflict with observational estimates of bar pattern speeds. Bar rotation
rates are typically classified by the dimensionless ratio
\begin{equation}
\Rot = \RCR/R_b\textrm{,}
\end{equation}
where \RCR{} is the radius of corotation and $R_b$ is the length of the
bar.\footnote{The radius of corotation \RCR{} is defined for circular orbits
as the radius at which the orbital frequency is equal to the pattern speed,
$\Omega_p$, of a given non-axisymmetric feature. In a galaxy with a constant
circular velocity $V_c$, it is given by $\RCR = V_c / \Omega_p$.} Galaxies
with $\Rot < 1.4$ are considered ``fast rotators'' while galaxies with $\Rot >
1.4$ are considered ``slow rotators.''\cite{2000ApJ...543..704D} Galaxies with
$\Rot < 1$ are not thought to be stable.\cite{1980AA....81..198C}
Observational estimates of the pattern speeds of bars indicate that nearly all
galaxies have $1 < \Rot < 1.4$.\cite{2011MSAIS..18...23C, 2015AA...576A.102A,
2019MNRAS.482.1733G}

@@

>>>>

The expectation that a dark matter halo acts to slow down a bar is in
conflict with observational estimates of bar pattern speeds. Bar rotation
rates are typically classified by the dimensionless ratio
\begin{equation}
\Rot = \RCR/R_b\textrm{,}
\end{equation}
where \RCR{} is the radius of corotation and $R_b$ is the length of the
bar.\footnote{The radius of corotation \RCR{} is defined for circular orbits
as the radius at which the orbital frequency is equal to the pattern speed,
$\Omega_p$, of a given non-axisymmetric feature. In a galaxy with a constant
circular velocity $V_c$, it is given by $\RCR = V_c / \Omega_p$.} Galaxies
with $\Rot < 1.4$ are considered ``fast rotators'' while galaxies with $\Rot >
1.4$ are considered ``slow rotators.''\cite{2000ApJ...543..704D} Galaxies with
$\Rot < 1$ are not thought to be stable.\cite{1980AA....81..198C}
Observational estimates of the pattern speeds of bars indicate that nearly all
galaxies have $1 < \Rot < 1.4$.\cite{2011MSAIS..18...23C, 2015AA...576A.102A,
2019MNRAS.482.1733G, 2020MNRAS.491.3655G}

@@

We note that ref.\cite{2020MNRAS.491.3655G} found that the rotation parameter
\Rot{} positively correlates with gas fraction, such that galaxies with higher
gas fractions are rotating more slowly. However, it is not obvious this is in
tension with our result since the gas fraction of galaxies correlates with
other galactic properties.\cite{2009ARAA..47..159B} Furthermore, the
measurement of pattern speeds is a delicate process still prone to large error
bars.
